When paying wirelessly with a credit card, there are rules for when to provide a PIN. One of the rules could be that you must always provide a PIN when the amount exceeds 350 DKK. Another could state that you -- regardless of the amount -- must provide a PIN at least every fourth transaction.

The method \methodname{Expend} in the following class has been developed to decide whether it is necessary to ask for a PIN:

\inputminted{csharp}{\context/question/Pin.cs}

\textbf{Subtask 1}

Investigate how the method \methodname{Expend} works.

\textbf{Subtask 2}

The code is built to comply with the two rules described at the beginning of this exercise. For each of these rules, you must now find the boundary cases. Boundary cases are those situations that define the edge of there a condition shifts between true or not. For example, 17 and 18 are boundary cases for some logic that determines whether a person has the right to vote (assuming that you have to be 18 to vote).

\textbf{Subtask 3}

Some rules are expressed in the problem text, and others may have arisen during the implementation. Create a test case that represents each combination of boundary values, and execute these test cases. Now verify that the method \methodname{Expend} works correctly by looking at the results of executing the program that you build from the test code.

\textbf{Subtask 4}

How would the testing strategy change if there was a random number generator in the picture such that the probability that you would be asked to provide a PIN code was 20\%?
