In this exercise, we raise the complexity a bit.

\begin{enumerate}
  \item Make sure to check out the \filename{progintro-exercises} repository in two locations of your filesystem. This is a way of simulating that multiple software developers are working on the same repository. Each have their own \idx{working copy}{Working copy!GIT}. In the following text, we are going to refer to these as directory A and directory B.
  \item Go to directory A, are replace the work \say{text} in each of the two last lines with the word \say{emphasis}. Commit the change, and push it.
    \begin{itemize}
      \item What would be a good commit message?
    \end{itemize}
  \item Go to directory B, and translate the last two lines to a (human) language of your choice. For Danish, this would be:
    \begin{minted}{markdown}
1. *italics* tekst.
2. **bold** tekst.
    \end{minted}
  \item Then save the file, commit the change and push the commit.
    \begin{itemize}
      \item What would be a good commit message?
    \end{itemize}
  \item If you have followed these istructions, you should have gotten an error message. Destribe what has happened, and try to draw it as a graph of commits.
  \item In order to solve the problem, we need to decide how to \idx{resolve}{Resoling} the situation:
    \begin{enumerate}
      \item Are we going to keep the version from B, and delete everything from A?
      \item Are we going to keep the version from A, and delete everything from B?
      \item Can we do a rewriting that honer both intentions (change of noun, and translation to different language)?
    \end{enumerate}
  \item Argue your choice.
  \item Make the necessary change, commit it, and push the commit.
  \item Verify on github that things are now in order.
  \item Check that your understanding of what has happened by interpreting githubs \say{network graph}. You may have to search a bit for it.
\end{enumerate}

