\section{Repetition}
\label{sec:flow:repetition}

% problem: print something once, twice, 1000 times, scalability problem, variable number of times
Let's say that we want to print out \say{Hello} once. This is a single trivial line of code. If we want to do it twice, then we can duplicate that line. That solution will still technically work if we want to print it out 1000 times, but then we are left with a 1000 line program that is hard to understand (lots of scrolling is necessary) and, frankly, quite boring. This is a problem of scalability. But it gets worse: Imagine that we have an integer variable that has been assigned a value from a user input, and we want to print out \say{Hello} this many times. As the concrete value isn't known at compile-time, the strategy of copying the line and pasting the right number of times simply cannot work.

\begin{syntaxfloat}
  \input{syntax/flow_repetition.tex}
  \caption{Statements for repetition}
  \label{syntax:flow:repetition}
\end{syntaxfloat}

\subsection{\keywordname{while}}

% highlevel concept: the while loop is the most fundamental loop, speaking aloud explanation (as long as a condition is true)

% figure: flowchart

\subsubsection{\csharp}

\subsection{\keywordname{do-while}}

% highlevel concept: speaking aloud explanation, notice that the statement comes before the condition, use this as a mnemonic device for the order of evaluation: the statement is evaluated first, this gives us an at-least-once property

% figure: flowchart

\subsubsection{\csharp}

\subsection{Converting Between \keywordname{while} and \keywordname{do-while}}

% intro: we now have two types of loops, hopefully it is intuitive when to choose one over the other, in some sense they seem very different, but we can convert one to the other

% figure: subfigure for each direction

% while-to-do-while: flowchart equivalency

% do-while-to-while:

\subsubsection{Problem of Repetition}

% motivation: so now we have two ways of doing the same thing, that begs the question: which option to go for? more importantly why should one option be chosen over the other? which qualities should we use for "scoring" each of the two options?
So, now we have two ways of doing (more or less) the same thing. That begs the question: Which option should we pick? More importantly, why should one option be chosen over the other? And which qualities should we use for \textsl{scoring} each of the two options?

% problem: two qualities stick out: readability and maintainability, readability essentially means how easy the code is to read and maintainability on the other hand boils down to how easy the code is to maintain, we can employ a number of (more or less well-defined) metrics for each, in this particular situation they both point in the same direction, this stems for one option having a duplicate element, for instance the way we went from a do-while to a while was to copy out a copy of the loop body before the loop, from a readability perspective this creates more lines burdens us with the need to recognize that those two pieces of code are identical and part of the same loop (this is explicit in the other option), from a maintainability perspective duplicated code is always risky as the developer is burdened with the need to manually keep the two copies in sync, any failure to do so will result in a bug, in summary unless you have a good reason not to you should simply use the most compact version
Two qualities stick out: Readability and maintainability. \defi{Readability}{Readability} essentially means how easy the code is to read, and \defi{maintainability}{Maintainability} boils down to how easy the code is to maintain. We can employ a number of (more or less well-defined) \idx{metrics}{Metric} for each. In this particular situation, they both happen to point in the same direction. This stems from one of the options having a duplicate element. For instance, the way we went from a do-while loop to a while loop was to place a copy of the loop body before the loop. From a readability perspective this creates mode lines of code, and it burdens us with the need to both recognize that those two pieces of code are identical and that they are part of the same loop. The latter part is explicit in the do-while option. From a maintainability perspective, duplicated code is always \idx{risky}{Risk} as the developer is burdened with the need to manually keep the two copies in \idx{sync}{Sync}. Any failure to do so will result in a bug. In summary, unless you have a good reason not to, you should simply use the most compact version.

\subsection{\keywordname{for}}

% common use case: it didn't take long for a common pattern of while loop usage to emerge, in this pattern a loop variable is declared before the loop, at the end of the loop this variable is adjusted and the condition checks whether this variable has passed some value
It didn't take long for a common \idx{pattern}{Pattern} of while loop usage to emerge. In this pattern, a loop variable is declared before the loop, at the end of the loop this variable is adjusted and the condition check whether this variable has passed some value. This is, for instance, how you would loop through all integers between two values.

% defining template: given this pattern a template can ben synthesized: initialization statement, condition, update statement, body, by generalizing the template we ensure that it is as applicable as possible, a new kind of loop -- the for loop -- is designed specifically to accommodate this template
If generalized, a template can be synthesized from this pattern. We ne an \idx{initialization statement}{Initialization statement}, a condition, an \idx{update statement}{Update statement}, and a body. The generalization comes from us using the generic construct of a statement for initialization and updates. Note that by choosing to build on statements, we also gain the option of having the initialization and update statements be expressed without any shared variables. By generalizing the template we ensure that it is as \idx{applicable}{Applicability} as possible. A new kind of loop -- the \keywordname{for} loop -- is designed specifically to accommodate this template.

\subsubsection{\csharp}

% how it is read aloud

\subsection{Control Structures}

\begin{syntaxfloat}
  \input{syntax/flow_repetition_control.tex}
  \caption{Control structures for repetition}
  \label{syntax:flow:repetition:control}
\end{syntaxfloat}

