\chapter{Namespaces}

% growth of code: so far most of the programs you have written has been small, maybe 10 lines of code (LoC), if you solve all the exercises of this book then you will write programs of more than 100 LoC, if you complete a software education you will likely participate if projects in excess of 1000 LoC, in the industry projects are often an order of magnitude or three larger, the linux kernel was in 2025 approx 40M LoC, most software projects grows over time as features are added and improvements are made
So far, most of the programs that you have written have been small. They are likely less than 20 line of code (\idx{LoC}{LoC}). If you solve all the exercises in this book then you will write programs of more than 100 LoC. If you complete a software education you will likely participate in projects in excess of 1000 LoC. In the \idx{industry}{Industry}, projects are often an order of magnitude or three larger. The Linux \idx{kernel}{Kernel} was in 2025 approx 40M LoC. Most software projects grow over time as feature are added and improvements made.

% clash of names: as the codebase grows so does the number and severity of problems stemming from that size, one of the very first problems you encounter is that of a name clash: you have found the right name for a variable or function and now you want to use the same name in a different context, the reasons are equally good but the compiler won't allow you to redefine the name, pure sadness, but what would it even mean? if you had two functions by the same name which implementation would be invoked when the name is called? given that there are two functions perhaps the choice of implementation should depend on where in the code the call site is located? and what about variables; when are they distinct and when are they the same? the situation appears to be a mess
As the \idx{codebase}{Codebase} grows so does the number and severity of problems stemming from that size. One of the very first problems that you encounter is that of a \idx{name clash}{Name clash}: You have found the right name for a variable or function, and now want to use the same name in a different \idx{context}{Context}. Your reasoning may be as good as for the first instance, but the \idx{compiler}{Compiler} won't allow you to \idx{redefine}{Name!Redefinition} the name. Pure sadness! But, what would it even mean? If you had two functions by the same name, which implementation would be \idx{invoked}{Invocation} when the name is called? Given that there two functions, perhaps the choice of implementation to invoke should depend on where in the code the call site is located? And what about variables; when are they distinct, and when  are they the same? The situation appears to be a mess.

% organization through namespaces: lets introduce some order to this chaos, up until now all the names that we have defined have existed within a single space, this is calles a namespace, conflicts in names are not allowed within a namespace, we can however have multiple namespaces and a name is allowed to be defined in multiple namespaces, when we refer to a name we either refer to the definition in the current namespace or we refer to it through the name of a different namespace, this mechanism allows us to name distinct variables and functions without having to worry about whether they are used elsewhere, sure if it is used closeby there could be an issue but then you should ask yourself whether both names are expressive enough
Let's introduce some order to this chaos. Up until now, all the names that we have defined have existed within a single space. This is called a \defi{namespace}{Namespace}. \idx{Conflicts}{Name!Conflict} in names are not allowed within a namespace; names have to be unique. We can, however, have multiple namespaces, and a name is allowed to be defined in multiple namespaces. When we refer to a name, we either refer to the definition in the current namespace, or we explicitly refer to it through the name of a different namespace. This mechanism allows us to name distinct variables and functions without having to worry about whether they are used elsewhere. Sure, if it is used close by, there could be an issue but then you should ask yourself whether both names are \idx{expressive}{Name!Expressiveness} enough.

\section{\csharp}

% intro: csharp's primary mechanism for implementing namespaces is called ... a namespace, syntax \ref{syntax:namespace} defines how to work with them
\csharp's primary mechanism for implementing namespaces is called \ldots\ a namespace. Syntax \ref{syntax:namespace} defines how we work with them.

\begin{syntaxfloat}
  \input{syntax/namespace.tex} % TODO: add how name can be name.name
  \caption{Namespaces}
  \label{syntax:namespace}
\end{syntaxfloat}

\subsection{Classes}

% full: technically, the class constructs that we used for structured data in section \ref{sec:primdata:struct} also represents namespaces, in section \ref{sec:objects} onwards we will dive deeper into what we can do with them, but in csharp terminology they are not namespaces
Technically, the \keywordname{class} construct that we used to define structured data in section \ref{sec:primdata:struct} is also a form of namespace, but in \csharp\ terminology they are not. In section \ref{sec:objects} onwards, we will dive deeper into what we can do with them.

