\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

% my background: classical (experimental) computer science, programming language tolerant, teaching object oriented programming (java and csharp) on a danish SE education, what is a danish SE education.
My background is from fairly classical (experimental) computer science, and has always been programming language tolerent. Today, I am teaching an introductionary programming course on a Danish software engineering education. That course has a focus on object-orientation. Previously, the it targeted Java, but we recently made the shift to \csharp.

% why c#?
\csharp\ (and Java for that matter) are languages that mix the fundamentals with a great amount of complexity. From what I see, students have a tendency to loose track of those fundamentals. So, why teach such langauges on the first course on programming? Well, only about half of a Danish software engineering education is computer science. The rest is project management, customer relations, requirement analysis and similar fields that are peripheral to programming. That means that some shortcuts have to be taken. And this is one.

% motivation: lack of introduction-level C# books that doesn't try to bypass the learning experience
Many \csharp\ books already exist, and quite a few of them claim to be aimed a novices. But as far as I can tell, they all bypass learning experiences that I feel are essential to informing the understanding of the student. This book is intended to fill that gap.
