The following link contains a list of airports in the world, with country code and coordinates: \scalebox{0.95}{\url{https://raw.githubusercontent.com/ip2location/ip2location-iata-icao/master/iata-icao.csv}}

\textbf{Subtask 1}

Copy the following code into a Livebook notebook (use multiple cells):
\inputminted[fontsize=\footnotesize]{elixir}{\context/question/airports.exs}

Three external modules are used:
\begin{itemize}
  \item \texttt{:req} to retrieve things from the internet.
  \item \texttt{:maplibre} to work with maps.
  \item \texttt{:kino\_maplibre} to display maps.
\end{itemize}

These modules must be added at the top under \say{Notebook dependencies and setup}. Select the latest versions of these modules.

You should now be able to click through the notebook and get a world map with a bunch of pins. You can zoom in in this map.

\textbf{Subtask 2}

What does the function \funcname{Req.get!} do?

\textbf{Subtask 3}

What is the role of \varname{index}?

\textbf{Subtask 4}

The module \modulename{Enum} has a \funcname{member?} function that tells whether a term is a member of a list. The same module has a \funcname{filter} function. Use a combination of these to ensure that only the airports located in a city from a country mentioned in \varname{countries\_interest} are shown.

\textbf{Subtask 5}

Now we need to color the markers according to the following rules:
\begin{itemize}
  \item Members of \varname{countries\_eu} should be colored \texttt{"blue"}.
  \item Members of \varname{countries\_efta} should be colored \texttt{"cyan"}.
  \item Members of \varname{countries\_eu\_cand} should be colored \texttt{"green"}.
  \item Members of \varname{countries\_enp} should be colored \texttt{"orange"}.
  \item Members of \varname{countries\_other} should be colored \texttt{"white"}.
\end{itemize}

Verify that it works!

\textbf{Subtask 6}

Why is \say{Heathrow Airport} not on the final map?
